A Large and Variable Leading Tail of Helium in a Hot Saturn Undergoing Runaway Inflation

### 2023-09-07 paper/paper1/ms.tex
orbital evolution

\edit1{\subsection{Prospect for orbital evolution}
  Content here...}

>>>>

\edit1{\subsection{Prospect for orbital evolution}
  Evaporating planets may lose a large fraction of their mass through Roche lobe overflow \citep{2014ApJ...793L...3V,2015ApJ...813..101V}.  These profoundly eroded planets should exhibit significant orbital evolution.  The extent and direction of such orbital evolution depends on the specific angular momentum loss, integrated over the mass loss history of the planet.  The observations presented here indicate a mass loss vector perpendicular to the orbit and towards the star.  We can reconstruct the starting orbit if we assume the current mass loss vector has been constant throughout its mass loss history.  Following \citet{2014ApJ...793L...3V} and \citet{2023ApJ...945L..36T} we can constrain the change in semi-major axis, a:
  \begin{equation}
    \frac{\dot{a}}{a} = -2 \frac{\dot{M}}{M}\left (1 - \frac{M}{M_\star} \right ).
  \end{equation}
}
